Reconstructing the neutron-star equation of state with gravitational-wave detectors from a realistic population of inspiralling binary neutron stars

### 2014-10-31 paper.tex
Added Affiliation for Ben.

\author{Benjamin D. Lackey$^1$, Leslie Wade$^2$}

\affiliation{
$^1$Department of Physics, Princeton University, Princeton, NJ 08544, USA\\
$^2$Department of Physics, University of Wisconsin--Milwaukee, P.O. Box 413, Milwaukee, Wisconsin 53201, USA
}

>>>>

\author{Benjamin D. Lackey$^{1, 2}$, Leslie Wade$^3$}

\affiliation{
$^1$Department of Physics, Princeton University, Princeton, NJ 08544, USA\\
$^2$Department of Physics, Syracuse University, Syracuse, NY 13244, USA\\
$^3$Department of Physics, University of Wisconsin--Milwaukee, P.O. Box 413, Milwaukee, Wisconsin 53201, USA
}
